---
title: "Translating all tweets into English with Google Translate API"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Translating tweets into English for topic modelling

Please note that the following code is only for documentation. A translated df will be provided in an anonymized version (i.e. without information about user names, user ids or tweet ids) in the GitHub repository. 

# Number of characters to be translated per week

```{r}
library(translateR)
library(tidyverse)
library(quanteda)
library(lubridate)
library(stringr)
library(dplyr)
library(googleLanguageR)
```

Translation is deliberately performed in chunks (per week) so that if translation does not work well, this will prevent using to many characters from the Google Translate API.

# Select only non-english texts for translation
```{r}
w_list <- list(w14, w15, w16, w17, w18, w19, w20, w21, w22)
w_ne_list <- lapply(w_list, function(x) x[x$lang != "en",])
```

## Create text IDs to match translated content to retweets
```{r}
w_tr_list <- list()

w_tr_list <- lapply(w_list, function(x) {
  x_tr <- as.data.frame(unique(x$text))
  x_tr <- tibble::rowid_to_column(x_tr, "textid")
  colnames(x_tr) <- c("textid", "text")
  x$textid <- x_tr$textid[match(x$text, x_tr$text)]
  return(x_tr)
})
```

# Remove https, Emojis, Hashtags and mentions
```{r}
w_tr_cleaned <- lapply(w_tr_list, function(x) {
  x$text_clean <- gsub("@","",x$text) # removes @ sign, but keeps usernames (for syntax)
  x$text_clean <- gsub("#", "",x$text_clean) # removes hashtag sign
  x$text_clean <- as.character(x$text_clean)
  x$text_clean <- gsub(" ?http[s]?://(?:[a-zA-Z]|[0-9]|[$-_@.&+]|[!*\\(\\),]|(?:%[0-9a-fA-F][0-9a-fA-F]))+", "",x$text_clean)
  x$text_clean <- iconv(x$text_clean, "UTF-8", "latin1", sub = "") # removes unicodes (emojis)
  x$text_clean <- str_squish(x$text_clean)
  return(x)
})
```

```{r}
# Create individual vector for each week
# Input for translation has to be a vector

w14vec <- as.vector(w_tr_cleaned[[1]]$text_clean)
w15vec <- as.vector(w_tr_cleaned[[2]]$text_clean)
w16vec <- as.vector(w_tr_cleaned[[3]]$text_clean)
w17vec <- as.vector(w_tr_cleaned[[4]]$text_clean)
w18vec <- as.vector(w_tr_cleaned[[5]]$text_clean)
w19vec <- as.vector(w_tr_cleaned[[6]]$text_clean)
w20vec <- as.vector(w_tr_cleaned[[7]]$text_clean)
w21vec <- as.vector(w_tr_cleaned[[8]]$text_clean)
w22vec <- as.vector(w_tr_cleaned[[9]]$text_clean)
```

# Translation

```{r}
# Auth
# gl_auth("ANONYMIZED")

# Translation (do each week individually - prevents using up API limits in case of errors)
w14_translated <- gl_translate(w14_vec, 
                               target = "en",
                               format = "text", 
                               source = "", 
                               model = "base") #translation

w14_translated$textid <- 0 # create Var for text id 
w14_translated$textid <- w14_tr$textid[match(w14_translated$text, w14_tr$text_clean)] # match text id

w15_translated <- gl_translate(w15_vec, 
                               target = "en",
                               format = "text", 
                               source = "", 
                               model = "base")

w15_translated$textid <- 0
w15_translated$textid <- w15_tr$textid[match(w15_translated$text, w15_tr$text_clean)]

w16_translated <- gl_translate(w16_vec, 
                               target = "en",
                               format = "text", 
                               source = "", 
                               model = "base")

w16_translated$textid <- 0
w16_translated$textid <- w16_tr$textid[match(w16_translated$text, w16_tr$text_clean)]

w17_translated <- gl_translate(w17_vec, 
                               target = "en",
                               format = "text", 
                               source = "", 
                               model = "base")

w17_translated$textid <- 0
w17_translated$textid <- w17_tr$textid[match(w17_translated$text, w17_tr$text_clean)]

w18_translated <- gl_translate(w18_vec, 
                               target = "en",
                               format = "text", 
                               source = "",
                               model = "base")

w18_translated$textid <- 0
w18_translated$textid <- w18_tr$textid[match(w18_translated$text, w18_tr$text_clean)]

w19_translated <- gl_translate(w19_vec, 
                               target = "en",
                               format = "text", 
                               source = "", 
                               model = "base")

w19_translated$textid <- 0
w19_translated$textid <- w19_tr$textid[match(w19_translated$text, w19_tr$text_clean)]

w20_translated <- gl_translate(w20_vec, 
                               target = "en",
                               format = "text", 
                               source = "", 
                               model = "base")

w20_translated$textid <- 0
w20_translated$textid <- w20_tr$textid[match(w20_translated$text, w20_tr$text_clean)]

w21_translated <- gl_translate(w21_vec, 
                               target = "en",
                               format = "text", 
                               source = "", 
                               model = "base")

w21_translated$textid <- 0
w21_translated$textid <- w21_tr$textid[match(w21_translated$text, w21_tr$text_clean)]

w22_translated <- gl_translate(w22_vec, 
                               target = "en",
                               format = "text", 
                               source = "", 
                               model = "base")

w22_translated$textid <- 0
w22_translated$textid <- w22_tr$textid[match(w22_translated$text, w22_tr$text_clean)]
```

# Match translated text into full data set via text id

```{r}
translated_list <- list(w14_translated, w15_translated, w16_translated, w17_translated, w18_translated, w19_translated, w20_translated, w21_translated, w22_translated)


# Use do.call and rbind to bind the individual data frames into one large data frame
w_tr_df <- do.call(rbind, w_tr_list)

# Create empty variable
w_tr_df$translated_text <- ""

# Match
w_tr_df <- lapply(translated_list, function(x) {
  x_translated_text <- x$translated_text
  x_textid <- x$textid
  df <- cbin(x_translated_text, x_textid)
  colnames(x_tr) <- c("translated_text", "textid")
  w_tr_df$translated <- x_tr$textid[match(x$text, x_tr$text)]
  return(w_tr_df)
})

```



