---
author: "Vivien Benert"
date: "30 3 2022"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(igraph)
library(dplyr)
```

# Community detection
There are various algorithms for community detection. For an overview see Stoltenberg et al. (2019).
Direction of edges is not necessarily important for the analysis of conflict lines. In other words: It does not matter whather A started a conversation with B about a topic X, it is only important that A and B talk about topic X. Thus, tie direction can be neglected when using community detection to investigate the salience of conflict lines in online debates. Stoltenberg et al. (2019) find that the Louvain algorithm provides good results in terms of interpretability of topic solution and modularity.

# Preparation for community detection
Turn networks into undirected networks for community detection.
```{r}
# Mentions
graph_mentions_collapse <- as.undirected(graph_mentions, mode = "collapse", edge.attr.comb = igraph_opt("edge.attr.comb")) # for community detection

graph_mentions_mutual <- as.undirected(graph_mentions, mode = "mutual", edge.attr.comb = igraph_opt("edge.attr.comb")) # only mutual ties kept (for RQ2)

# Retweets
graph_retweets_collapse <- as.undirected(graph_retweets, mode = "collapse", edge.attr.comb = igraph_opt("edge.attr.comb"))

graph_retweets_mutual <- as.undirected(graph_retweets, mode = "mutual", edge.attr.comb = igraph_opt("edge.attr.comb"))

# Quotes
graph_quotes_collapse <- as.undirected(graph_quotes, mode = "collapse", edge.attr.comb = igraph_opt("edge.attr.comb"))

graph_quotes_mutual <- as.undirected(graph_quotes, mode = "mutual", edge.attr.comb = igraph_opt("edge.attr.comb"))

# Replies
graph_replies_collapse <- as.undirected(graph_replies, mode = "collapse", edge.attr.comb = igraph_opt("edge.attr.comb"))

graph_replies_mutual <- as.undirected(graph_replies, mode = "mutual", edge.attr.comb = igraph_opt("edge.attr.comb"))
```

# Louvain community detection
```{r}
# Mentions
louvain_mentions <- cluster_louvain(graph_mentions_collapse)
V(graph_mentions)$louvain <- louvain_mentions$membership

# Retweets
louvain_retweets <- cluster_louvain(graph_retweets_collapse)
V(graph_retweets)$louvain <- louvain_retweets$membership

# Quotes
louvain_quotes <- cluster_louvain(graph_quotes_collapse)
V(graph_quotes)$louvain <- louvain_quotes$membership

# Retweets
louvain_replies <- cluster_louvain(graph_replies_collapse)
V(graph_replies)$louvain <- louvain_replies$membership
```

# Community membership in nodelists matchen
```{r}
# Louvain
x <- as.data.frame(louvain_replies$names)
y <- as.data.frame(louvain_replies$membership)
louvain_replies_df <- cbind(x,y)
colnames(louvain_replies_df) <- c("name", "louvain")

nodelist_df$louvain_replies <- 0
nodelist_df$louvain_replies <- louvain_replies_df$louvain[match(nodelist_df$name, louvain_replies_df$name)]


x <- as.data.frame(louvain_quotes$names)
y <- as.data.frame(louvain_quotes$membership)
louvain_quotes_df <- cbind(x,y)
colnames(louvain_quotes_df) <- c("name", "louvain")

nodelist_df$louvain_quotes <- 0
nodelist_df$louvain_quotes <- louvain_quotes_df$louvain[match(nodelist_df$name, louvain_quotes_df$name)]


x <- as.data.frame(louvain_retweets$names)
y <- as.data.frame(louvain_retweets$membership)
louvain_retweets_df <- cbind(x,y)
colnames(louvain_retweets_df) <- c("name", "louvain")

nodelist_df$louvain_retweets <- 0
nodelist_df$louvain_retweets <- louvain_retweets_df$louvain[match(nodelist_df$name, louvain_retweets_df$name)]


x <- as.data.frame(louvain_mentions$names)
y <- as.data.frame(louvain_mentions$membership)
louvain_mentions_df <- cbind(x,y)
colnames(louvain_mentions_df) <- c("name", "louvain")

nodelist_df$louvain_mentions <- 0
nodelist_df$louvain_mentions <- louvain_mentions_df$louvain[match(nodelist_df$name, louvain_mentions_df$name)]
```

# Descriptive analysis of community structures
```{r}
sort(table(nodelist_df$louvain_mentions), decreasing=T)
# Communities with more than 100 members
# 381, 134, 13, 5, 136, 751, 277, 130, 742, 746, 129, 50, 284, 7, 696, 141, 132, 133, 729, 10, 428, 801, 244, 477, 416, 142, 166, 148, 135, 1100, 208, 829

sort(table(nodelist_df$louvain_retweets), decreasing=T)
# Communities with more than 100 members
# 39, 48, 31, 10, 917, 21, 139, 569, 865, 835, 140, 111, 221, 8, 17, 24, 1023, 26, 260, 50, 945, 80, 836, 902, 201, 44, 9, 353, 845, 101, 89, 503, 196, 77, 96, 1170, 1080, 1267, 646, 455, 432, 968, 110, 933

sort(table(nodelist_df$louvain_quotes), decreasing=T)
# Communities with more than 100 members
# 572, 261, 374, 1213, 1106, 676, 1108, 1337, 1022, 397, 838, 1144, 1358, 407, 693, 544, 740, 1292, 677, 1184, 334, 1177, 1023, 1215

sort(table(nodelist_df$louvain_replies), decreasing=T)
# Communities with more than 100 members
# 1806, 1556, 1431, 1208, 1205, 1316, 930, 1206, 1546, 1178, 1298, 1698, 1611, 1053
```

# STM tt tr matchen
```{r}
# load tt_tr_stm object
tt_tr_stm$louvain_mentions <- 0
tt_tr_stm$louvain_mentions <- louvain_mentions_df$louvain[match(tt_tr_stm$screen_name, louvain_mentions_df$name)]

tt_tr_stm$louvain_retweets <- 0
tt_tr_stm$louvain_retweets <- louvain_retweets_df$louvain[match(tt_tr_stm$screen_name, louvain_retweets_df$name)]

tt_tr_stm$louvain_quotes <- 0
tt_tr_stm$louvain_quotes <- louvain_quotes_df$louvain[match(tt_tr_stm$screen_name, louvain_quotes_df$name)]

tt_tr_stm$louvain_replies <- 0
tt_tr_stm$louvain_replies <- louvain_replies_df$louvain[match(tt_tr_stm$screen_name, louvain_replies_df$name)]
```

# Subset data:
All communities with at least 100 nodes for in depth analysis.
```{r}
names(nodelist_df)
nodelist_louvain_mentions <- nodelist_df[which(nodelist_df$louvain_mentions==381 | nodelist_df$louvain_mentions==134 | nodelist_df$louvain_mentions==13 | nodelist_df$louvain_mentions==5 | nodelist_df$louvain_mentions==136 | nodelist_df$louvain_mentions==751 | nodelist_df$louvain_mentions==277 | nodelist_df$louvain_mentions==130 | nodelist_df$louvain_mentions==742 | nodelist_df$louvain_mentions==746 | nodelist_df$louvain_mentions==129 | nodelist_df$louvain_mentions==50 | nodelist_df$louvain_mentions==284 | nodelist_df$louvain_mentions==7 | nodelist_df$louvain_mentions==696 | nodelist_df$louvain_mentions==141 | nodelist_df$louvain_mentions==132 | nodelist_df$louvain_mentions==133 | nodelist_df$louvain_mentions==729 | nodelist_df$louvain_mentions==10 | nodelist_df$louvain_mentions==428 | nodelist_df$louvain_mentions==801 | nodelist_df$louvain_mentions==244 | nodelist_df$louvain_mentions==477 | nodelist_df$louvain_mentions==416 | nodelist_df$louvain_mentions==142 | nodelist_df$louvain_mentions==166 | nodelist_df$louvain_mentions==148 | nodelist_df$louvain_mentions==135 | nodelist_df$louvain_mentions==1100 | nodelist_df$louvain_mentions==208 | nodelist_df$louvain_mentions==829),]

nodelist_louvain_retweets <- nodelist_df[which(nodelist_df$louvain_retweets==39| nodelist_df$louvain_retweets==48| nodelist_df$louvain_retweets==31| nodelist_df$louvain_retweets==10| nodelist_df$louvain_retweets==917| nodelist_df$louvain_retweets==21| nodelist_df$louvain_retweets==139| nodelist_df$louvain_retweets==569| nodelist_df$louvain_retweets==865| nodelist_df$louvain_retweets==835| nodelist_df$louvain_retweets==140| nodelist_df$louvain_retweets==111| nodelist_df$louvain_retweets==221| nodelist_df$louvain_retweets==8| nodelist_df$louvain_retweets==17| nodelist_df$louvain_retweets==24| nodelist_df$louvain_retweets==1023| nodelist_df$louvain_retweets==26| nodelist_df$louvain_retweets==260| nodelist_df$louvain_retweets==50| nodelist_df$louvain_retweets==945| nodelist_df$louvain_retweets==80| nodelist_df$louvain_retweets==836| nodelist_df$louvain_retweets==902| nodelist_df$louvain_retweets==201| nodelist_df$louvain_retweets==44| nodelist_df$louvain_retweets==9| nodelist_df$louvain_retweets==353| nodelist_df$louvain_retweets==845| nodelist_df$louvain_retweets==101| nodelist_df$louvain_retweets==89| nodelist_df$louvain_retweets==503| nodelist_df$louvain_retweets==196| nodelist_df$louvain_retweets==77| nodelist_df$louvain_retweets==96| nodelist_df$louvain_retweets==1170| nodelist_df$louvain_retweets==1080| nodelist_df$louvain_retweets==1267| nodelist_df$louvain_retweets==646| nodelist_df$louvain_retweets==455| nodelist_df$louvain_retweets==432| nodelist_df$louvain_retweets==968| nodelist_df$louvain_retweets==110| nodelist_df$louvain_retweets==933),]

nodelist_louvain_quotes <- nodelist_df[which(nodelist_df$louvain_quotes==572| nodelist_df$louvain_quotes==261| nodelist_df$louvain_quotes==374| nodelist_df$louvain_quotes==1213| nodelist_df$louvain_quotes==1106| nodelist_df$louvain_quotes==676| nodelist_df$louvain_quotes==1108| nodelist_df$louvain_quotes==1337| nodelist_df$louvain_quotes==1022| nodelist_df$louvain_quotes==397| nodelist_df$louvain_quotes==838| nodelist_df$louvain_quotes==1144| nodelist_df$louvain_quotes==1358| nodelist_df$louvain_quotes==407| nodelist_df$louvain_quotes==693| nodelist_df$louvain_quotes==544| nodelist_df$louvain_quotes==740| nodelist_df$louvain_quotes==1292| nodelist_df$louvain_quotes==677| nodelist_df$louvain_quotes==1184| nodelist_df$louvain_quotes==334| nodelist_df$louvain_quotes==1177| nodelist_df$louvain_quotes==1023| nodelist_df$louvain_quotes==1215),]

nodelist_louvain_replies <- nodelist_df[which(nodelist_df$louvain_replies==1806| nodelist_df$louvain_replies==1556| nodelist_df$louvain_replies==1431| nodelist_df$louvain_replies==1208| nodelist_df$louvain_replies==1205| nodelist_df$louvain_replies==1316| nodelist_df$louvain_replies==930| nodelist_df$louvain_replies==1206| nodelist_df$louvain_replies==1546| nodelist_df$louvain_replies==1178| nodelist_df$louvain_replies==1298| nodelist_df$louvain_replies==1698| nodelist_df$louvain_replies==1611| nodelist_df$louvain_replies==1053),]
```

# Recode 0 to NA for descritive anaylsis
```{r}
# Mentions Louvain
which(nodelist_louvain_mentions$actor_group==0)
nodelist_louvain_mentions$actor_group <- ifelse(nodelist_louvain_mentions$actor_group==0, NA, nodelist_louvain_mentions$actor_group)

which(nodelist_louvain_mentions$pol_leaning==0)
nodelist_louvain_mentions$pol_leaning <- ifelse(nodelist_louvain_mentions$pol_leaning==0, NA, nodelist_louvain_mentions$pol_leaning)

which(nodelist_louvain_mentions$pol_act==0)
nodelist_louvain_mentions$pol_act <- ifelse(nodelist_louvain_mentions$pol_act==0, NA, nodelist_louvain_mentions$pol_act)

which(nodelist_louvain_mentions$med_act==0)
nodelist_louvain_mentions$med_act <- ifelse(nodelist_louvain_mentions$med_act==0, NA, nodelist_louvain_mentions$med_act)

which(nodelist_louvain_mentions$civ_act==0)
nodelist_louvain_mentions$civ_act <- ifelse(nodelist_louvain_mentions$civ_act==0, NA, nodelist_louvain_mentions$civ_act)

which(nodelist_louvain_mentions$scope==0)
nodelist_louvain_mentions$scope <- ifelse(nodelist_louvain_mentions$scope==0, NA, nodelist_louvain_mentions$scope)

# Retweets Louvain
which(nodelist_louvain_retweets$actor_group==0)
nodelist_louvain_retweets$actor_group <- ifelse(nodelist_louvain_retweets$actor_group==0, NA, nodelist_louvain_retweets$actor_group)

which(nodelist_louvain_retweets$pol_leaning==0)
nodelist_louvain_retweets$pol_leaning <- ifelse(nodelist_louvain_retweets$pol_leaning==0, NA, nodelist_louvain_retweets$pol_leaning)

which(nodelist_louvain_retweets$pol_act==0)
nodelist_louvain_retweets$pol_act <- ifelse(nodelist_louvain_retweets$pol_act==0, NA, nodelist_louvain_retweets$pol_act)

which(nodelist_louvain_retweets$med_act==0)
nodelist_louvain_retweets$med_act <- ifelse(nodelist_louvain_retweets$med_act==0, NA, nodelist_louvain_retweets$med_act)

which(nodelist_louvain_retweets$civ_act==0)
nodelist_louvain_retweets$civ_act <- ifelse(nodelist_louvain_retweets$civ_act==0, NA, nodelist_louvain_retweets$civ_act)

which(nodelist_louvain_retweets$scope==0)
nodelist_louvain_retweets$scope <- ifelse(nodelist_louvain_retweets$scope==0, NA, nodelist_louvain_retweets$scope)

# Quotes
which(nodelist_louvain_quotes$actor_group==0)
nodelist_louvain_quotes$actor_group <- ifelse(nodelist_louvain_quotes$actor_group==0, NA, nodelist_louvain_quotes$actor_group)

which(nodelist_louvain_quotes$pol_leaning==0)
nodelist_louvain_quotes$pol_leaning <- ifelse(nodelist_louvain_quotes$pol_leaning==0, NA, nodelist_louvain_quotes$pol_leaning)

which(nodelist_louvain_quotes$pol_act==0)
nodelist_louvain_quotes$pol_act <- ifelse(nodelist_louvain_quotes$pol_act==0, NA, nodelist_louvain_quotes$pol_act)

which(nodelist_louvain_quotes$med_act==0)
nodelist_louvain_quotes$med_act <- ifelse(nodelist_louvain_quotes$med_act==0, NA, nodelist_louvain_quotes$med_act)

which(nodelist_louvain_quotes$civ_act==0)
nodelist_louvain_quotes$civ_act <- ifelse(nodelist_louvain_quotes$civ_act==0, NA, nodelist_louvain_quotes$civ_act)

which(nodelist_louvain_quotes$scope==0)
nodelist_louvain_quotes$scope <- ifelse(nodelist_louvain_quotes$scope==0, NA, nodelist_louvain_quotes$scope)

# Replies
which(nodelist_louvain_replies$actor_group==0)
nodelist_louvain_replies$actor_group <- ifelse(nodelist_louvain_replies$actor_group==0, NA, nodelist_louvain_replies$actor_group)

which(nodelist_louvain_replies$pol_leaning==0)
nodelist_louvain_replies$pol_leaning <- ifelse(nodelist_louvain_replies$pol_leaning==0, NA, nodelist_louvain_replies$pol_leaning)

which(nodelist_louvain_replies$pol_act==0)
nodelist_louvain_replies$pol_act <- ifelse(nodelist_louvain_replies$pol_act==0, NA, nodelist_louvain_replies$pol_act)

which(nodelist_louvain_replies$med_act==0)
nodelist_louvain_replies$med_act <- ifelse(nodelist_louvain_replies$med_act==0, NA, nodelist_louvain_replies$med_act)

which(nodelist_louvain_replies$civ_act==0)
nodelist_louvain_replies$civ_act <- ifelse(nodelist_louvain_replies$civ_act==0, NA, nodelist_louvain_replies$civ_act)

which(nodelist_louvain_replies$scope==0)
nodelist_louvain_replies$scope <- ifelse(nodelist_louvain_replies$scope==0, NA, nodelist_louvain_replies$scope)
```

# Description of communities: cross tables
```{r}
library(descr)
library(dplyr)
```

```{r}
# Mentions
ct <- descr::CrossTable(nodelist_louvain_mentions$actor_group, nodelist_louvain_mentions$louvain_mentions, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=F, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")
ct_mtrx <- descr:::CreateNewTab(ct)
write.csv2(ct_mtrx,"FF3_deskr_actor group distribution in largest mention communities_LOUVAIN.csv")

ct <- descr::CrossTable(nodelist_louvain_mentions$pol_leaning, nodelist_louvain_mentions$louvain_mentions, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=F, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")
ct_mtrx <- descr:::CreateNewTab(ct)
write.csv2(ct_mtrx,"FF3_deskr_pol leaning distribution in largest mentions communities_LOUVAIN.csv")

ct <- descr::CrossTable(nodelist_louvain_mentions$pol_act, nodelist_louvain_mentions$louvain_mentions, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=F, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")
ct_mtrx <- descr:::CreateNewTab(ct)
write.csv2(ct_mtrx,"FF3_deskr_political actor distribution in largest mentions communities_LOUVAIN.csv")

ct <- descr::CrossTable(nodelist_louvain_mentions$civ_act, nodelist_louvain_mentions$louvain_mentions, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=F, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")
ct_mtrx <- descr:::CreateNewTab(ct)
write.csv2(ct_mtrx,"FF3_deskr_civil society distribution in largest mentions communities_LOUVAIN.csv")

ct <- descr::CrossTable(nodelist_louvain_mentions$med_act, nodelist_louvain_mentions$louvain_mentions, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=F, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")
ct_mtrx <- descr:::CreateNewTab(ct)
write.csv2(ct_mtrx,"FF3_deskr_media actor distribution in largest mentions communities_LOUVAIN.csv")

# Repeat for other networks
```

# STM distribution in communities
```{r}
# Mentions Louvain
x <- tt_tr_stm %>% group_by(louvain_mentions)

# Nochmal Summen pro Akteur aus tt_tr_stm (um retweets zu ber端cksichtigen)
y <- x %>% summarise(
  t_1 = sum(Topic1),
  t_2 = sum(Topic2),
  t_3 = sum(Topic3),
  t_4 = sum(Topic4),
  t_5 = sum(Topic5),
  t_6 = sum(Topic6),
  t_7 = sum(Topic7),
  t_8 = sum(Topic8),
  t_9 = sum(Topic9),
  t_10 = sum(Topic10),
  t_11 = sum(Topic11),
  t_12 = sum(Topic12),
  t_13 = sum(Topic13),
  t_14 = sum(Topic14),
  t_15 = sum(Topic15),
  t_16 = sum(Topic16),
  t_17 = sum(Topic17),
  t_18 = sum(Topic18),
  t_19 = sum(Topic19),
  t_20 = sum(Topic20),
  t_21 = sum(Topic21),
  t_22 = sum(Topic22),
  t_23 = sum(Topic23),
  t_24 = sum(Topic24),
  t_25 = sum(Topic25)
)

y$total <- rowSums(y[, c(2:26)]) # row sum = number of Tweets!
# Jede Spalte durch Anzahl der Tweets teilen, dann nochmal rosum=100!
z <- as.data.frame(y)
z <- z[,2:26]/z[,27] 
z$total <- rowSums(z[, c(1:25)]) # passt!
colnames(y) <- c("community","sum_1","sum_2","sum_3","sum_4", "sum_5", "sum_6", "sum_7", "sum_8", "sum_9", "sum_10", "sum_11", "sum_12", "sum_13", "sum_14", "sum_15", "sum_16", "sum_17", "sum_18", "sum_19", "sum_20", "sum_21", "sum_22", "sum_23", "sum_24", "sum_25", "no_tweets")
stm_mentions_louvain <- cbind(y, z)
```

```{r}
# Retweets Louvain
x <- tt_tr_stm %>% group_by(louvain_retweets)

# Nochmal Summen pro Akteur aus tt_tr_stm (um retweets zu ber端cksichtigen)
y <- x %>% summarise(
  t_1 = sum(Topic1),
  t_2 = sum(Topic2),
  t_3 = sum(Topic3),
  t_4 = sum(Topic4),
  t_5 = sum(Topic5),
  t_6 = sum(Topic6),
  t_7 = sum(Topic7),
  t_8 = sum(Topic8),
  t_9 = sum(Topic9),
  t_10 = sum(Topic10),
  t_11 = sum(Topic11),
  t_12 = sum(Topic12),
  t_13 = sum(Topic13),
  t_14 = sum(Topic14),
  t_15 = sum(Topic15),
  t_16 = sum(Topic16),
  t_17 = sum(Topic17),
  t_18 = sum(Topic18),
  t_19 = sum(Topic19),
  t_20 = sum(Topic20),
  t_21 = sum(Topic21),
  t_22 = sum(Topic22),
  t_23 = sum(Topic23),
  t_24 = sum(Topic24),
  t_25 = sum(Topic25)
)

y$total <- rowSums(y[, c(2:26)]) # row sum = number of Tweets!
# Jede Spalte durch Anzahl der Tweets teilen, dann nochmal rosum=100!
z <- as.data.frame(y)
z <- z[,2:26]/z[,27] 
z$total <- rowSums(z[, c(1:25)]) # passt!
colnames(y) <- c("community","sum_1","sum_2","sum_3","sum_4", "sum_5", "sum_6", "sum_7", "sum_8", "sum_9", "sum_10", "sum_11", "sum_12", "sum_13", "sum_14", "sum_15", "sum_16", "sum_17", "sum_18", "sum_19", "sum_20", "sum_21", "sum_22", "sum_23", "sum_24", "sum_25", "no_tweets")
stm_retweets_louvain <- cbind(y, z)
```

```{r}
# Quotes Louvain
x <- tt_tr_stm %>% group_by(louvain_quotes)

# Nochmal Summen pro Akteur aus tt_tr_stm (um retweets zu ber端cksichtigen)
y <- x %>% summarise(
  t_1 = sum(Topic1),
  t_2 = sum(Topic2),
  t_3 = sum(Topic3),
  t_4 = sum(Topic4),
  t_5 = sum(Topic5),
  t_6 = sum(Topic6),
  t_7 = sum(Topic7),
  t_8 = sum(Topic8),
  t_9 = sum(Topic9),
  t_10 = sum(Topic10),
  t_11 = sum(Topic11),
  t_12 = sum(Topic12),
  t_13 = sum(Topic13),
  t_14 = sum(Topic14),
  t_15 = sum(Topic15),
  t_16 = sum(Topic16),
  t_17 = sum(Topic17),
  t_18 = sum(Topic18),
  t_19 = sum(Topic19),
  t_20 = sum(Topic20),
  t_21 = sum(Topic21),
  t_22 = sum(Topic22),
  t_23 = sum(Topic23),
  t_24 = sum(Topic24),
  t_25 = sum(Topic25)
)

y$total <- rowSums(y[, c(2:26)]) # row sum = number of Tweets!
# Jede Spalte durch Anzahl der Tweets teilen, dann nochmal rosum=100!
z <- as.data.frame(y)
z <- z[,2:26]/z[,27] 
z$total <- rowSums(z[, c(1:25)]) # passt!
colnames(y) <- c("community","sum_1","sum_2","sum_3","sum_4", "sum_5", "sum_6", "sum_7", "sum_8", "sum_9", "sum_10", "sum_11", "sum_12", "sum_13", "sum_14", "sum_15", "sum_16", "sum_17", "sum_18", "sum_19", "sum_20", "sum_21", "sum_22", "sum_23", "sum_24", "sum_25", "no_tweets")
stm_quotes_louvain <- cbind(y, z)
```

```{r}
# Replies Louvain
x <- tt_tr_stm %>% group_by(louvain_replies)

# Nochmal Summen pro Akteur aus tt_tr_stm (um retweets zu ber端cksichtigen)
y <- x %>% summarise(
  t_1 = sum(Topic1),
  t_2 = sum(Topic2),
  t_3 = sum(Topic3),
  t_4 = sum(Topic4),
  t_5 = sum(Topic5),
  t_6 = sum(Topic6),
  t_7 = sum(Topic7),
  t_8 = sum(Topic8),
  t_9 = sum(Topic9),
  t_10 = sum(Topic10),
  t_11 = sum(Topic11),
  t_12 = sum(Topic12),
  t_13 = sum(Topic13),
  t_14 = sum(Topic14),
  t_15 = sum(Topic15),
  t_16 = sum(Topic16),
  t_17 = sum(Topic17),
  t_18 = sum(Topic18),
  t_19 = sum(Topic19),
  t_20 = sum(Topic20),
  t_21 = sum(Topic21),
  t_22 = sum(Topic22),
  t_23 = sum(Topic23),
  t_24 = sum(Topic24),
  t_25 = sum(Topic25)
)

y$total <- rowSums(y[, c(2:26)]) # row sum = number of Tweets!
# Jede Spalte durch Anzahl der Tweets teilen, dann nochmal rosum=100!
z <- as.data.frame(y)
z <- z[,2:26]/z[,27] 
z$total <- rowSums(z[, c(1:25)]) # passt!
colnames(y) <- c("community","sum_1","sum_2","sum_3","sum_4", "sum_5", "sum_6", "sum_7", "sum_8", "sum_9", "sum_10", "sum_11", "sum_12", "sum_13", "sum_14", "sum_15", "sum_16", "sum_17", "sum_18", "sum_19", "sum_20", "sum_21", "sum_22", "sum_23", "sum_24", "sum_25", "no_tweets")
stm_replies_louvain <- cbind(y, z)
```

# Density of communities
```{r}
# Check community is set as node attribute
vertex_attr(graph_mentions) #yes

# List of objects in environment to call
objects <- ls()
objects <- objects[1:77]

# Create empty data frame
community_sizes <- data.frame(matrix(ncol=4, nrow=0))
colnames(community_sizes) <- c("community", "nodes", "edges", "density")

for (i in 1:length(objects)) {
  x <- get(objects[i], envir = as.environment(-1), mode = "any",
    inherits = FALSE)
  a <- gorder(x)
  b <- gsize(x)
  c <- edge_density(x)
  new <- data.frame("community"= i, "nodes" = a, "edges" = b, "density" = c)
  community_sizes <- rbind(community_sizes, new)
}

y <- as.data.frame(objects)
community_sizes <- cbind(y, community_sizes)
```
