---
title: "Auswertung Diss_FF2_deskriptiv"
author: "Vivien Benert"
date: "30 8 2022"
output:
  pdf_document: default
  html_document: default
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(igraph)
library(dplyr)
library(descr)

# Data: graphs can be created from edgelist and nodelist
```

# Create graphs with reciprocated edges
```{r}
# Write logical vector whether edge is reciprocated as edge attribute
E(graph_mentions)$is_mutual <- which_mutual(graph_mentions, es=E(graph_mentions))
E(graph_retweets)$is_mutual <- which_mutual(graph_retweets, es=E(graph_retweets))
E(graph_quotes)$is_mutual <- which_mutual(graph_quotes, es=E(graph_quotes))
E(graph_replies)$is_mutual <- which_mutual(graph_replies, es=E(graph_replies))

# Subgraph with only reciprocated edges
graph_mentions_recip <- subgraph.edges(graph_mentions, E(graph_mentions)[E(graph_mentions)$is_mutual==TRUE])
graph_retweets_recip <- subgraph.edges(graph_retweets, E(graph_retweets)[E(graph_retweets)$is_mutual==TRUE])
graph_quotes_recip <- subgraph.edges(graph_quotes, E(graph_quotes)[E(graph_quotes)$is_mutual==TRUE])
graph_replies_recip <- subgraph.edges(graph_replies, E(graph_replies)[E(graph_replies)$is_mutual==TRUE])
```

# Create edgelists and nodelists
```{r}
nodelist_mentions_recip <- as_data_frame(graph_mentions_recip, what="vertices")
nodelist_retweets_recip <- as_data_frame(graph_retweets_recip, what="vertices")
nodelist_quotes_recip <- as_data_frame(graph_quotes_recip, what="vertices")
nodelist_replies_reip <- as_data_frame(graph_replies_recip, what="vertices")

edgelist_mentions_recip <- as_long_data_frame(graph_mentions_recip)
edgelist_retweets_recip <- as_long_data_frame(graph_retweets_recip)
edgelist_quotes_recip <- as_long_data_frame(graph_quotes_recip)
edgelist_replies_recip <- as_long_data_frame(graph_replies_recip)
```

# Descriptive Analysis
```{r}
# Frequencies of senofs and receivers by actor group and political leaning
# Mentions
freq(edgelist_mentions_recip$from_actor_group, user.missing=0)
freq(edgelist_mentions_recip$to_actor_group, user.missing=0)
freq(edgelist_mentions_recip$from_pol_leaning, user.missing=c(0, 999))
freq(edgelist_mentions_recip$to_pol_leaning, user.missing=c(0, 999))
```

```{r}
# Frequencies of senofs and receivers by actor group and political leaning
# Retweets
freq(edgelist_retweets_recip$from_actor_group, user.missing=0)
freq(edgelist_retweets_recip$to_actor_group, user.missing=0)
freq(edgelist_retweets_recip$from_pol_leaning, user.missing=c(0, 999))
freq(edgelist_retweets_recip$to_pol_leaning, user.missing=c(0, 999))
```

```{r}
# Frequencies of senofs and receivers by actor group and political leaning
# Quotes
freq(edgelist_quotes_recip$from_actor_group, user.missing=0)
freq(edgelist_quotes_recip$to_actor_group, user.missing=0)
freq(edgelist_quotes_recip$from_pol_leaning, user.missing=c(0, 999))
freq(edgelist_quotes_recip$to_pol_leaning, user.missing=c(0, 999))
```

```{r}
# Frequencies of senofs and receivers by actor group and political leaning
# Replies
freq(edgelist_replies_recip$from_actor_group, user.missing=0)
freq(edgelist_replies_recip$to_actor_group, user.missing=0)
freq(edgelist_replies_recip$from_pol_leaning, user.missing=c(0, 999))
freq(edgelist_replies_recip$to_pol_leaning, user.missing=c(0, 999))
```

# Cross Tabs
```{r}
# Recode 0 to NA for Crosstabs
edgelist_mentions_recip[edgelist_mentions_recip==0] <- NA
edgelist_retweets_recip[edgelist_retweets_recip==0] <- NA
edgelist_quotes_recip[edgelist_quotes_recip==0] <- NA
edgelist_replies_recip[edgelist_replies_recip==0] <- NA

edgelist_mentions[edgelist_mentions==0] <- NA
edgelist_retweets[edgelist_retweets==0] <- NA
edgelist_quotes[edgelist_quotes==0] <- NA
edgelist_replies[edgelist_replies==0] <- NA
```

```{r}
# Actor groups
descr::CrossTable(edgelist_mentions_recip$to_actor_group, edgelist_mentions_recip$from_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")

# Pol leaning
descr::CrossTable(edgelist_mentions_recip$to_pol_leaning, edgelist_mentions_recip$from_pol_leaning, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")

# From pol leaning to actor group
descr::CrossTable(edgelist_mentions_recip$to_actor_group, edgelist_mentions_recip$from_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")
```

# Subquestion 1: Who addresses European politicians most often?
```{r}
# MENTIONS
# Subset of edges to European level politicians
edgelist_mentions_EUpol <- edgelist_mentions[which(edgelist_mentions$to_actor_group==10
& (edgelist_mentions$to_scope==2 | edgelist_mentions$to_scope==3)),]

edgelist_mentions_EUpol[edgelist_mentions_EUpol==0] <- NA

# Freq: Actor groups addressing European level politicians
freq(edgelist_mentions_EUpol$from_actor_group, user.missing=c(0, 999))

# Freq: Edge Scope of edges to European level politicians
freq(edgelist_mentions_EUpol$edge_scope_new, user.missing=c(0, 999))

# Crosstab: From actor group by pol leaning
descr::CrossTable(edgelist_mentions_EUpol$from_pol_leaning, edgelist_mentions_EUpol$from_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")

# Crosstab: From actor group by edge scope
descr::CrossTable(edgelist_mentions_EUpol$edge_scope_new, edgelist_mentions_EUpol$from_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")
```

```{r}
# Retweets
# Subset of edges to European level politicians
edgelist_retweets_EUpol <- edgelist_retweets[which(edgelist_retweets$to_actor_group==10
& (edgelist_retweets$to_scope==2 | edgelist_retweets$to_scope==3)),]

edgelist_retweets_EUpol[edgelist_retweets_EUpol==0] <- NA

# Freq: Actor groups addressing European level politicians
freq(edgelist_retweets_EUpol$from_actor_group, user.missing=c(0, 999))

# Freq: Edge Scope of edges to European level politicians
freq(edgelist_retweets_EUpol$edge_scope_new, user.missing=c(0, 999))

# Crosstab: From actor group by pol leaning
descr::CrossTable(edgelist_retweets_EUpol$from_pol_leaning, edgelist_retweets_EUpol$from_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")

# Crosstab: From actor group by edge scope
descr::CrossTable(edgelist_retweets_EUpol$edge_scope_new, edgelist_retweets_EUpol$from_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")
```

```{r}
# Quotes
# Subset of edges to European level politicians
edgelist_quotes_EUpol <- edgelist_quotes[which(edgelist_quotes$to_actor_group==10
& (edgelist_quotes$to_scope==2 | edgelist_quotes$to_scope==3)),]

edgelist_quotes_EUpol[edgelist_quotes_EUpol==0] <- NA

# Freq: Actor groups addressing European level politicians
freq(edgelist_quotes_EUpol$from_actor_group, user.missing=c(0, 999))

# Freq: Edge Scope of edges to European level politicians
freq(edgelist_quotes_EUpol$edge_scope_new, user.missing=c(0, 999))

# Crosstab: From actor group by pol leaning
descr::CrossTable(edgelist_quotes_EUpol$from_pol_leaning, edgelist_quotes_EUpol$from_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")

# Crosstab: From actor group by edge scope
descr::CrossTable(edgelist_quotes_EUpol$edge_scope_new, edgelist_quotes_EUpol$from_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")
```

```{r}
# Replies
# Subset of edges to European level politicians
edgelist_replies_EUpol <- edgelist_replies[which(edgelist_replies$to_actor_group==10
& (edgelist_replies$to_scope==2 | edgelist_replies$to_scope==3)),]

edgelist_replies_EUpol[edgelist_replies_EUpol==0] <- NA

# Freq: Actor groups addressing European level politicians
freq(edgelist_replies_EUpol$from_actor_group, user.missing=c(0, 999))

# Freq: Edge Scope of edges to European level politicians
freq(edgelist_replies_EUpol$edge_scope_new, user.missing=c(0, 999))

# Crosstab: From actor group by pol leaning
descr::CrossTable(edgelist_replies_EUpol$from_pol_leaning, edgelist_replies_EUpol$from_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")

# Crosstab: From actor group by edge scope
ct <- descr::CrossTable(edgelist_replies_EUpol$edge_scope_new, edgelist_replies_EUpol$from_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")
```

# Subquestion 2: Who addresses European politicians most often?
```{r}
# Subset national politicians
edgelist_mentions_natpol <- edgelist_mentions[which(edgelist_mentions$to_actor_group==10
& edgelist_mentions$to_scope==1),]

edgelist_mentions_natpol[edgelist_mentions_natpol==0] <- NA

# Freq: Actor groups addressing national level politicians
freq(edgelist_mentions_natpol$from_actor_group, user.missing=c(0, 999))

# Freq: Edge Scope of edges to national level politicians
freq(edgelist_mentions_natpol$edge_scope_new, user.missing=c(0, 999))

# Crosstab: From actor group by pol leaning
descr::CrossTable(edgelist_mentions_natpol$from_pol_leaning, edgelist_mentions_natpol$from_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")

# Crosstab: From actor group by edge scope
descr::CrossTable(edgelist_mentions_natpol$edge_scope_new, edgelist_mentions_natpol$from_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")
```

```{r}
# Subset national politicians
edgelist_retweets_natpol <- edgelist_retweets[which(edgelist_retweets$to_actor_group==10
& edgelist_retweets$to_scope==1),]

edgelist_retweets_natpol[edgelist_retweets_natpol==0] <- NA

# Freq: Actor groups addressing national level politicians
freq(edgelist_retweets_natpol$from_actor_group, user.missing=c(0, 999))

# Freq: Edge Scope of edges to national level politicians
freq(edgelist_retweets_natpol$edge_scope_new, user.missing=c(0, 999))

# Crosstab: From actor group by pol leaning
descr::CrossTable(edgelist_retweets_natpol$from_pol_leaning, edgelist_retweets_natpol$from_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")

# Crosstab: From actor group by edge scope
descr::CrossTable(edgelist_retweets_natpol$edge_scope_new, edgelist_retweets_natpol$from_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")
```

```{r}
# Subset national politicians
edgelist_quotes_natpol <- edgelist_quotes[which(edgelist_quotes$to_actor_group==10
& edgelist_quotes$to_scope==1),]

edgelist_quotes_natpol[edgelist_quotes_natpol==0] <- NA

# Freq: Actor groups addressing national level politicians
freq(edgelist_quotes_natpol$from_actor_group, user.missing=c(0, 999))

# Freq: Edge Scope of edges to national level politicians
freq(edgelist_quotes_natpol$edge_scope_new, user.missing=c(0, 999))

# Crosstab: From actor group by pol leaning
descr::CrossTable(edgelist_quotes_natpol$from_pol_leaning, edgelist_quotes_natpol$from_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")

# Crosstab: From actor group by edge scope
descr::CrossTable(edgelist_quotes_natpol$edge_scope_new, edgelist_quotes_natpol$from_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")
```

```{r}
# Subset national politicians
edgelist_replies_natpol <- edgelist_replies[which(edgelist_replies$to_actor_group==10
& edgelist_replies$to_scope==1),]

edgelist_replies_natpol[edgelist_replies_natpol==0] <- NA

# Freq: Actor groups addressing national level politicians
freq(edgelist_replies_natpol$from_actor_group, user.missing=c(0, 999))

# Freq: Edge Scope of edges to national level politicians
freq(edgelist_replies_natpol$edge_scope_new, user.missing=c(0, 999))

# Crosstab: From actor group by pol leaning
descr::CrossTable(edgelist_replies_natpol$from_pol_leaning, edgelist_replies_natpol$from_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")

# Crosstab: From actor group by edge scope
descr::CrossTable(edgelist_replies_natpol$edge_scope_new, edgelist_replies_natpol$from_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")
```

# Subquestion 3: Percentage of reciprocated ties with European politicians
Which percantages of ties to European politicians are reciprocated?
```{r}
# Subset reciprocated ties to European level politicians
edgelist_mentions_recip_EUpol <- edgelist_mentions_recip[which(edgelist_mentions_recip$to_actor_group==10
& (edgelist_mentions_recip$to_scope==2 | edgelist_mentions_recip$to_scope==3)),]

edgelist_mentions_recip_EUpol[edgelist_mentions_recip_EUpol==0] <- NA

# Reciprocated edges to EU Pol Act by actor group
freq(edgelist_mentions_recip_EUpol$from_actor_group, user.missing=c(0, 999))
freq(edgelist_mentions_recip_EUpol$from_pol_leaning, user.missing=c(0, 999))
freq(edgelist_mentions_recip_EUpol$from_civ_act, user.missing=c(0, 999))
freq(edgelist_mentions_recip_EUpol$edge_scope_new, user.missing=c(0, 999))

# Recprocated ties to EU pol act by pol leaning of actor group
 descr::CrossTable(edgelist_mentions_recip_EUpol$from_pol_leaning, edgelist_mentions_recip_EUpol$from_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")

# Edge scope reziproker Beziehungen to EU pol act je actor group
descr::CrossTable(edgelist_mentions_recip_EUpol$edge_scope_new, edgelist_mentions_recip_EUpol$from_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")
```

```{r}
# Subset reciprocated ties to European level politicians
edgelist_retweets_recip_EUpol <- edgelist_retweets_recip[which(edgelist_retweets_recip$to_actor_group==10
& (edgelist_retweets_recip$to_scope==2 | edgelist_retweets_recip$to_scope==3)),]

edgelist_retweets_recip_EUpol[edgelist_retweets_recip_EUpol==0] <- NA

# Reciprocated edges to EU Pol Act by actor group
freq(edgelist_retweets_recip_EUpol$from_actor_group, user.missing=c(0, 999))
freq(edgelist_retweets_recip_EUpol$from_pol_leaning, user.missing=c(0, 999))
freq(edgelist_retweets_recip_EUpol$from_civ_act, user.missing=c(0, 999))
freq(edgelist_retweets_recip_EUpol$edge_scope_new, user.missing=c(0, 999))

# Reciprocated edges to  EU pol act by pol leaning of actor group
descr::CrossTable(edgelist_retweets_recip_EUpol$from_pol_leaning, edgelist_retweets_recip_EUpol$from_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")

# Edge scope of reciprocated edges to EU pol act by actor group
descr::CrossTable(edgelist_retweets_recip_EUpol$edge_scope_new, edgelist_retweets_recip_EUpol$from_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")
```

```{r}
# Subset reciprocated ties to European level politicians
edgelist_quotes_recip_EUpol <- edgelist_quotes_recip[which(edgelist_quotes_recip$to_actor_group==10
& (edgelist_quotes_recip$to_scope==2 | edgelist_quotes_recip$to_scope==3)),]

edgelist_quotes_recip_EUpol[edgelist_quotes_recip_EUpol==0] <- NA

# Reciprocated edges to EU Pol Act by actor group
freq(edgelist_quotes_recip_EUpol$from_actor_group, user.missing=c(0, 999))
freq(edgelist_quotes_recip_EUpol$from_pol_leaning, user.missing=c(0, 999))
freq(edgelist_quotes_recip_EUpol$from_civ_act, user.missing=c(0, 999))
freq(edgelist_quotes_recip_EUpol$edge_scope_new, user.missing=c(0, 999))

# Reciprocated edges to EU pol act by pol leaning of actor group
descr::CrossTable(edgelist_quotes_recip_EUpol$from_pol_leaning, edgelist_quotes_recip_EUpol$from_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")

# Edge scope of reciprocated edges to EU pol act by actor group
descr::CrossTable(edgelist_quotes_recip_EUpol$edge_scope_new, edgelist_quotes_recip_EUpol$from_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")
```

```{r}
# Subset reciprocated ties to European level politicians
edgelist_replies_recip_EUpol <- edgelist_replies_recip[which(edgelist_replies_recip$to_actor_group==10
& (edgelist_replies_recip$to_scope==2 | edgelist_replies_recip$to_scope==3)),]

edgelist_replies_recip_EUpol[edgelist_replies_recip_EUpol==0] <- NA

# Reciprocated edges to EU Pol Act by actor group
freq(edgelist_replies_recip_EUpol$from_actor_group, user.missing=c(0, 999))
freq(edgelist_replies_recip_EUpol$from_pol_leaning, user.missing=c(0, 999))
freq(edgelist_replies_recip_EUpol$from_civ_act, user.missing=c(0, 999))
freq(edgelist_replies_recip_EUpol$edge_scope_new, user.missing=c(0, 999))

# Reciprocated edges to  EU pol act by pol leaning of actor group
descr::CrossTable(edgelist_replies_recip_EUpol$from_pol_leaning, edgelist_replies_recip_EUpol$from_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")

# Edge scope of reciprocated edges to EU pol act by actor group
descr::CrossTable(edgelist_replies_recip_EUpol$edge_scope_new, edgelist_replies_recip_EUpol$from_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")
```

# Reciprocated edges to national politcians

```{r}
# Subset reciprocated ties to national level politicians
edgelist_mentions_recip_natpol <- edgelist_mentions_recip[which(edgelist_mentions_recip$to_actor_group==10
& edgelist_mentions_recip$to_scope==1),]

edgelist_mentions_recip_natpol[edgelist_mentions_recip_natpol==0] <- NA

# Reciprocated edges to national Pol Act by actor group
freq(edgelist_mentions_recip_natpol$from_actor_group, user.missing=c(0, 999))
freq(edgelist_mentions_recip_natpol$from_pol_leaning, user.missing=c(0, 999))
freq(edgelist_mentions_recip_natpol$from_civ_act, user.missing=c(0, 999))
freq(edgelist_mentions_recip_natpol$edge_scope_new, user.missing=c(0, 999))

# Reciprocated edges to national pol act by pol leaning of actor group
descr::CrossTable(edgelist_mentions_recip_natpol$from_pol_leaning, edgelist_mentions_recip_natpol$from_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")

# Edge scope of reciprocated edges to national pol act by actor group
descr::CrossTable(edgelist_mentions_recip_natpol$edge_scope_new, edgelist_mentions_recip_natpol$from_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")
```

```{r}
# Subset reciprocated ties to national level politicians
edgelist_retweets_recip_natpol <- edgelist_retweets_recip[which(edgelist_retweets_recip$to_actor_group==10
& edgelist_retweets_recip$to_scope==1),]

edgelist_retweets_recip_natpol[edgelist_retweets_recip_natpol==0] <- NA

# Reciprocated edges to national Pol Act by actor group
freq(edgelist_retweets_recip_natpol$from_actor_group, user.missing=c(0, 999))
freq(edgelist_retweets_recip_natpol$from_pol_leaning, user.missing=c(0, 999))
freq(edgelist_retweets_recip_natpol$from_civ_act, user.missing=c(0, 999))
freq(edgelist_retweets_recip_natpol$edge_scope_new, user.missing=c(0, 999))

# Reciprocated edges to national pol act by pol leaning of actor group
descr::CrossTable(edgelist_retweets_recip_natpol$from_pol_leaning, edgelist_retweets_recip_natpol$from_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")

# Edge scope of reciprocated edges to national pol act by actor group
descr::CrossTable(edgelist_retweets_recip_natpol$edge_scope_new, edgelist_retweets_recip_natpol$from_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")
```

```{r}
# Subset reciprocated ties to national level politicians
edgelist_quotes_recip_natpol <- edgelist_quotes_recip[which(edgelist_quotes_recip$to_actor_group==10
& edgelist_quotes_recip$to_scope==1),]

edgelist_quotes_recip_natpol[edgelist_quotes_recip_natpol==0] <- NA

# Reciprocated edges to national Pol Act nach actor group
freq(edgelist_quotes_recip_natpol$from_actor_group, user.missing=c(0, 999))
freq(edgelist_quotes_recip_natpol$from_pol_leaning, user.missing=c(0, 999))
freq(edgelist_quotes_recip_natpol$from_civ_act, user.missing=c(0, 999))
freq(edgelist_quotes_recip_natpol$edge_scope_new, user.missing=c(0, 999))

# Reciprocated edges to national pol act by pol leaning of actor group
descr::CrossTable(edgelist_quotes_recip_natpol$from_pol_leaning, edgelist_quotes_recip_natpol$from_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")

# Edge scope of reciprocated edges to national pol act by actor group
descr::CrossTable(edgelist_quotes_recip_natpol$edge_scope_new, edgelist_quotes_recip_natpol$from_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")
```

```{r}
# Subset reciprocated ties to national level politicians
edgelist_replies_recip_natpol <- edgelist_replies_recip[which(edgelist_replies_recip$to_actor_group==10
& edgelist_replies_recip$to_scope==1),]

edgelist_replies_recip_natpol[edgelist_replies_recip_natpol==0] <- NA

# Reciprocated edges to national pol act by actor group
freq(edgelist_replies_recip_natpol$from_actor_group, user.missing=c(0, 999))
freq(edgelist_replies_recip_natpol$from_pol_leaning, user.missing=c(0, 999))
freq(edgelist_replies_recip_natpol$from_civ_act, user.missing=c(0, 999))
freq(edgelist_replies_recip_natpol$edge_scope_new, user.missing=c(0, 999))

# Reciprocated edges to national pol act by pol leaning of actor group
descr::CrossTable(edgelist_replies_recip_natpol$from_pol_leaning, edgelist_replies_recip_natpol$from_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")

# Edge scope of reciprocated edges to national pol act by actor group
descr::CrossTable(edgelist_replies_recip_natpol$edge_scope_new, edgelist_replies_recip_natpol$from_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")
```

# Subquestion 4: Direct communication of European politicians to citizens
How often do European politicians address civil society and citizens?

```{r}
# Subset ties FROM European level politicians
edgelist_mentions_from_EUpol <- edgelist_mentions[which(edgelist_mentions$from_actor_group==10
& (edgelist_mentions$from_scope==2 | edgelist_mentions$from_scope==3)),]

# Edges from EU Pol Act to actor group
freq(edgelist_mentions_from_EUpol$to_actor_group, user.missing=c(0, 999))
# Edges from EU Pol Act to pol leaning
freq(edgelist_mentions_from_EUpol$to_pol_leaning, user.missing=c(0, 999))
# Edges from EU Pol Act to civil society actors
freq(edgelist_mentions_from_EUpol$to_civ_act, user.missing=c(0, 999))

# Edges from European pol act to Actor group by pol leaning
descr::CrossTable(edgelist_mentions_from_EUpol$to_pol_leaning, edgelist_mentions_from_EUpol$to_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")

# Edges from European pol act to civil society group by pol leaning
descr::CrossTable(edgelist_mentions_from_EUpol$to_pol_leaning, edgelist_mentions_from_EUpol$to_civ_act, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")

# Edge scope of edges from European pol act to Actor group
descr::CrossTable(edgelist_mentions_from_EUpol$edge_scope_new, edgelist_mentions_from_EUpol$to_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")
```

```{r}
# Subset ties FROM European level politicians
edgelist_retweets_from_EUpol <- edgelist_retweets[which(edgelist_retweets$from_actor_group==10
& (edgelist_retweets$from_scope==2 | edgelist_retweets$from_scope==3)),]

# Edges from EU Pol Act to actor group
freq(edgelist_retweets_from_EUpol$to_actor_group, user.missing=c(0, 999))
# Edges from EU Pol Act to pol leaning
freq(edgelist_retweets_from_EUpol$to_pol_leaning, user.missing=c(0, 999))
# Edges from EU Pol Act to civil society actors
freq(edgelist_retweets_from_EUpol$to_civ_act, user.missing=c(0, 999))

# Edges from European pol act to Actor group by pol leaning
descr::CrossTable(edgelist_retweets_from_EUpol$to_pol_leaning, edgelist_retweets_from_EUpol$to_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")

# Edges from European pol act to civil society group by pol leaning
descr::CrossTable(edgelist_retweets_from_EUpol$to_pol_leaning, edgelist_retweets_from_EUpol$to_civ_act, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")

# Edge scope of edges from European pol act to Actor group
descr::CrossTable(edgelist_retweets_from_EUpol$edge_scope_new, edgelist_retweets_from_EUpol$to_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")
```

```{r}
# Subset ties FROM European level politicians
edgelist_quotes_from_EUpol <- edgelist_quotes[which(edgelist_quotes$from_actor_group==10
& (edgelist_quotes$from_scope==2 | edgelist_quotes$from_scope==3)),]

# Edges from EU Pol Act to actor group
freq(edgelist_quotes_from_EUpol$to_actor_group, user.missing=c(0, 999))
# Edges from EU Pol Act to pol leaning
freq(edgelist_quotes_from_EUpol$to_pol_leaning, user.missing=c(0, 999))
# Edges from EU Pol Act to civil society actors
freq(edgelist_quotes_from_EUpol$to_civ_act, user.missing=c(0, 999))

# Edges from European pol act to Actor group by pol leaning
descr::CrossTable(edgelist_quotes_from_EUpol$to_pol_leaning, edgelist_quotes_from_EUpol$to_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")

# Edges from European pol act to civil society group by pol leaning
descr::CrossTable(edgelist_quotes_from_EUpol$to_pol_leaning, edgelist_quotes_from_EUpol$to_civ_act, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")

# Edge scope of edges from European pol act to Actor group
descr::CrossTable(edgelist_quotes_from_EUpol$edge_scope_new, edgelist_quotes_from_EUpol$to_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")
```


```{r}
# Subset ties FROM European level politicians
edgelist_replies_from_EUpol <- edgelist_replies[which(edgelist_replies$from_actor_group==10
& (edgelist_replies$from_scope==2 | edgelist_replies$from_scope==3)),]

# Edges from EU Pol Act to actor group
freq(edgelist_replies_from_EUpol$to_actor_group, user.missing=c(0, 999))
# Edges from EU Pol Act to pol leaning
freq(edgelist_replies_from_EUpol$to_pol_leaning, user.missing=c(0, 999))
# Edges from EU Pol Act to civil society actors
freq(edgelist_replies_from_EUpol$to_civ_act, user.missing=c(0, 999))

# Edges from European pol act to Actor group by pol leaning
descr::CrossTable(edgelist_replies_from_EUpol$to_pol_leaning, edgelist_replies_from_EUpol$to_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")

# Edges from European pol act to civil society group by pol leaning
descr::CrossTable(edgelist_replies_from_EUpol$to_pol_leaning, edgelist_replies_from_EUpol$to_civ_act, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")

# Edge scope of Edges from European pol act to Actor group
descr::CrossTable(edgelist_replies_from_EUpol$edge_scope_new, edgelist_replies_from_EUpol$to_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")
```

# Subquestion 5: Direct communication of national politicians to citizens
How often do national politicians address civil society and citizens?
```{r}
# Subset ties FROM national level politicians
edgelist_mentions_from_natpol <- edgelist_mentions[which(edgelist_mentions$from_actor_group==10
& edgelist_mentions$from_scope==1),]

# Edges from national Pol Act to actor group
freq(edgelist_mentions_from_natpol$to_actor_group, user.missing=c(0, 999))

# Edges from national Pol Act to pol leaning
freq(edgelist_mentions_from_natpol$to_pol_leaning, user.missing=c(0, 999))

# Edges from national Pol Act to civil society actors
freq(edgelist_mentions_from_natpol$to_civ_act, user.missing=c(0, 999))

# Edges from national pol act to Actor group by pol leaning
descr::CrossTable(edgelist_mentions_from_natpol$to_pol_leaning, edgelist_mentions_from_natpol$to_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")

# Edges from national pol act to civil society group by pol leaning
descr::CrossTable(edgelist_mentions_from_natpol$to_pol_leaning, edgelist_mentions_from_natpol$to_civ_act, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")

# Edge scope of Edges from national pol act to Actor group
descr::CrossTable(edgelist_mentions_from_natpol$edge_scope_new, edgelist_mentions_from_natpol$to_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")
```

```{r}
# Subset ties FROM national level politicians
edgelist_retweets_from_natpol <- edgelist_retweets[which(edgelist_retweets$from_actor_group==10
& edgelist_retweets$from_scope==1),]

# Edges from national Pol Act to actor group
freq(edgelist_retweets_from_natpol$to_actor_group, user.missing=c(0, 999))
# Edges from national Pol Act to pol leaning
freq(edgelist_retweets_from_natpol$to_pol_leaning, user.missing=c(0, 999))
# Edges from national Pol Act to civil society actors
freq(edgelist_retweets_from_natpol$to_civ_act, user.missing=c(0, 999))

# Edges from national pol act to Actor group by pol leaning
descr::CrossTable(edgelist_retweets_from_natpol$to_pol_leaning, edgelist_retweets_from_natpol$to_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")

# Edges from national pol act to civil society group by pol leaning
descr::CrossTable(edgelist_retweets_from_natpol$to_pol_leaning, edgelist_retweets_from_natpol$to_civ_act, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")

# Edge scope of Edges from national pol act to Actor group
descr::CrossTable(edgelist_retweets_from_natpol$edge_scope_new, edgelist_retweets_from_natpol$to_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")
```

```{r}
# Subset ties FROM national level politicians
edgelist_quotes_from_natpol <- edgelist_quotes[which(edgelist_quotes$from_actor_group==10
& edgelist_quotes$from_scope==1),]

# Edges from national Pol Act to actor group
freq(edgelist_quotes_from_natpol$to_actor_group, user.missing=c(0, 999))

# Edges from national Pol Act to pol leaning
freq(edgelist_quotes_from_natpol$to_pol_leaning, user.missing=c(0, 999))

# Edges from national Pol Act to civil society actors
freq(edgelist_quotes_from_natpol$to_civ_act, user.missing=c(0, 999))

# Edges from national pol act to Actor group by pol leaning
descr::CrossTable(edgelist_quotes_from_natpol$to_pol_leaning, edgelist_quotes_from_natpol$to_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")

# Edges from national pol act to civil society group by pol leaning
descr::CrossTable(edgelist_quotes_from_natpol$to_pol_leaning, edgelist_quotes_from_natpol$to_civ_act, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")

# Edge scope of Edges from national pol act to Actor group
descr::CrossTable(edgelist_quotes_from_natpol$edge_scope_new, edgelist_quotes_from_natpol$to_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")
```

```{r}
# Subset ties FROM national level politicians
edgelist_replies_from_natpol <- edgelist_replies[which(edgelist_replies$from_actor_group==10
& edgelist_replies$from_scope==1),]

# Edges from national Pol Act to actor group
freq(edgelist_replies_from_natpol$to_actor_group, user.missing=c(0, 999))

# Edges from national Pol Act to pol leaning
freq(edgelist_replies_from_natpol$to_pol_leaning, user.missing=c(0, 999))

# Edges from national Pol Act to civil society actors
freq(edgelist_replies_from_natpol$to_civ_act, user.missing=c(0, 999))

# Edges from national pol act to Actor group by pol leaning
descr::CrossTable(edgelist_replies_from_natpol$to_pol_leaning, edgelist_replies_from_natpol$to_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")

# Edges from national pol act to civil society group by pol leaning
descr::CrossTable(edgelist_replies_from_natpol$to_pol_leaning, edgelist_replies_from_natpol$to_civ_act, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")

# Edge scope of Edges from national pol act to Actor group
descr::CrossTable(edgelist_replies_from_natpol$edge_scope_new, edgelist_replies_from_natpol$to_actor_group, digits=2, max.width = 5, expected=FALSE, prop.r=F, prop.c=TRUE, prop.t=F, prop.chisq=FALSE, chisq = FALSE, format = "SPSS")
```

# Subquestion 6: Comparison of topic agendas citizens/civil society and politicians
Load topic model data tt_tr_stm und nodelist_df_stm

# Group STM by actor group
```{r}
x <- tt_tr_stm %>% group_by(actor_group)

y <- x %>% summarise(
  t_1 = sum(Topic1),
  t_2 = sum(Topic2),
  t_3 = sum(Topic3),
  t_4 = sum(Topic4),
  t_5 = sum(Topic5),
  t_6 = sum(Topic6),
  t_7 = sum(Topic7),
  t_8 = sum(Topic8),
  t_9 = sum(Topic9),
  t_10 = sum(Topic10),
  t_11 = sum(Topic11),
  t_12 = sum(Topic12),
  t_13 = sum(Topic13),
  t_14 = sum(Topic14),
  t_15 = sum(Topic15),
  t_16 = sum(Topic16),
  t_17 = sum(Topic17),
  t_18 = sum(Topic18),
  t_19 = sum(Topic19),
  t_20 = sum(Topic20),
  t_21 = sum(Topic21),
  t_22 = sum(Topic22),
  t_23 = sum(Topic23),
  t_24 = sum(Topic24),
  t_25 = sum(Topic25))

y$total <- rowSums(y[, c(2:26)]) # row sum = number of tweets
z <- as.data.frame(y)
z <- z[,2:26]/z[,27] 
z$total <- rowSums(z[, c(1:25)])
colnames(y) <- c("actor_group","sum_1","sum_2","sum_3","sum_4", "sum_5", "sum_6", "sum_7", "sum_8", "sum_9", "sum_10", "sum_11", "sum_12", "sum_13", "sum_14", "sum_15", "sum_16", "sum_17", "sum_18", "sum_19", "sum_20", "sum_21", "sum_22", "sum_23", "sum_24", "sum_25", "no_tweets")
topics_actors <- cbind(y, z)
```

# Get topic agendas of national and European politicians
```{r}
# Subset data by political actors
tt_tr_stm_politicians <- tt_tr_stm[which(tt_tr_stm$actor_group==10),]
View(tt_tr_stm_politicians)
tt_tr_stm_politicians$scope_v2 <- ifelse(tt_tr_stm_politicians$scope==2 | tt_tr_stm_politicians$scope==3, 3, tt_tr_stm_politicians$scope)
```

# Group by scope
```{r}
x <- tt_tr_stm_politicians %>% group_by(scope_v2)

y <- x %>% summarise(
  t_1 = sum(Topic1),
  t_2 = sum(Topic2),
  t_3 = sum(Topic3),
  t_4 = sum(Topic4),
  t_5 = sum(Topic5),
  t_6 = sum(Topic6),
  t_7 = sum(Topic7),
  t_8 = sum(Topic8),
  t_9 = sum(Topic9),
  t_10 = sum(Topic10),
  t_11 = sum(Topic11),
  t_12 = sum(Topic12),
  t_13 = sum(Topic13),
  t_14 = sum(Topic14),
  t_15 = sum(Topic15),
  t_16 = sum(Topic16),
  t_17 = sum(Topic17),
  t_18 = sum(Topic18),
  t_19 = sum(Topic19),
  t_20 = sum(Topic20),
  t_21 = sum(Topic21),
  t_22 = sum(Topic22),
  t_23 = sum(Topic23),
  t_24 = sum(Topic24),
  t_25 = sum(Topic25)
)

y$total <- rowSums(y[, c(2:26)])
z <- as.data.frame(y)
z <- z[,2:26]/z[,27] 
z$total <- rowSums(z[, c(1:25)]) 
colnames(y) <- c("scope","sum_1","sum_2","sum_3","sum_4", "sum_5", "sum_6", "sum_7", "sum_8", "sum_9", "sum_10", "sum_11", "sum_12", "sum_13", "sum_14", "sum_15", "sum_16", "sum_17", "sum_18", "sum_19", "sum_20", "sum_21", "sum_22", "sum_23", "sum_24", "sum_25", "no_tweets")
topics_politicians <- cbind(y, z)
```

# Get topic agendas of national and European civil society
```{r}
# Subset data by political actors
tt_tr_stm_civil <- tt_tr_stm[which(tt_tr_stm$actor_group==30),]
tt_tr_stm_civil$scope_v2 <- ifelse(tt_tr_stm_civil$scope==2 | tt_tr_stm_civil$scope==3, 3, tt_tr_stm_civil$scope)
```

# Group by scope
```{r}
x <- tt_tr_stm_civil %>% group_by(scope_v2)

y <- x %>% summarise(
  t_1 = sum(Topic1),
  t_2 = sum(Topic2),
  t_3 = sum(Topic3),
  t_4 = sum(Topic4),
  t_5 = sum(Topic5),
  t_6 = sum(Topic6),
  t_7 = sum(Topic7),
  t_8 = sum(Topic8),
  t_9 = sum(Topic9),
  t_10 = sum(Topic10),
  t_11 = sum(Topic11),
  t_12 = sum(Topic12),
  t_13 = sum(Topic13),
  t_14 = sum(Topic14),
  t_15 = sum(Topic15),
  t_16 = sum(Topic16),
  t_17 = sum(Topic17),
  t_18 = sum(Topic18),
  t_19 = sum(Topic19),
  t_20 = sum(Topic20),
  t_21 = sum(Topic21),
  t_22 = sum(Topic22),
  t_23 = sum(Topic23),
  t_24 = sum(Topic24),
  t_25 = sum(Topic25)
)

y$total <- rowSums(y[, c(2:26)])
z <- as.data.frame(y)
z <- z[,2:26]/z[,27] 
z$total <- rowSums(z[, c(1:25)])
colnames(y) <- c("scope","sum_1","sum_2","sum_3","sum_4", "sum_5", "sum_6", "sum_7", "sum_8", "sum_9", "sum_10", "sum_11", "sum_12", "sum_13", "sum_14", "sum_15", "sum_16", "sum_17", "sum_18", "sum_19", "sum_20", "sum_21", "sum_22", "sum_23", "sum_24", "sum_25", "no_tweets")
topics_civil <- cbind(y, z)
```

# Transpose df for (spearman) correlation
```{r}
names(topics_actors)
topics_actors <- topics_actors[, c(1, 28:52)]
topics_civil <- topics_civil[, c(1, 28:52)]
topics_politicians <- topics_politicians[, c(1, 28:52)]

# transpose
topics_actors <- t(topics_actors)
colnames(topics_actors) <- c("null", "political_actors", "economic_actors", "civil_society", "media", "cultural_actors", "citizens", "other", "unavailable")
topics_actors <- topics_actors[-1,] # delete first row
View(topics_actors)
topics_actors <- as.data.frame(topics_actors)

topics_civil <- t(topics_civil)
colnames(topics_civil) <- c("national", "European", "international", "global", "unclear")
topics_civil <- topics_civil[-1,] # delete first row
View(topics_civil)
topics_civil_df <- as.data.frame(topics_civil)

topics_politicians <- t(topics_politicians)
colnames(topics_politicians) <- c("national", "European", "global", "unclear")
topics_politicians <- topics_politicians[-1,] # delete first row
View(topics_politicians)
topics_politicians_df <- as.data.frame(topics_politicians)
```

# New dfs
```{r}
politicians <- as.data.frame(topics_actors_df$political_actors)
civil_society <- as.data.frame(topics_actors_df$civil_society)
citizens <- as.data.frame(topics_actors_df$citizens)
media <- as.data.frame(topics_actors_df$media)

politicians_national <- as.data.frame(topics_politicians_df$national)
politicians_europen <- as.data.frame(topics_politicians_df$European)

civil_national <- as.data.frame(topics_civil_df$national)
civil_european <- as.data.frame(topics_civil_df$European)

# Bind
topics_corr_total <- cbind(politicians, civil_society, media, citizens)
# Citizens and politcians
topics_corr_pol_cit <- cbind(politicians_national, politicians_europen, citizens)
# Civil society and politicians 
topics_corr_pol_civ <- cbind(politicians_national, politicians_europen, civil_national, civil_european)
```

# Subquestion 7: Correlations of topics proportions by actor groups
```{r}
#Pearson
pearson_matrix_total <- round(cor(topics_corr_total),
  digits = 3) # rounded to 3 decimals
pearson_matrix_pol_cit <- round(cor(topics_corr_pol_cit),
  digits = 3) # rounded to 3 decimals
pearson_matrix_pol_civ <- round(cor(topics_corr_pol_civ),
  digits = 3) # rounded to 3 decimals
```